{Hierarchy Builder:}\\ {Algebraic hierarchies} \\ {made easy} {in {\sc Coq} with {\sc Elpi}}

### 2020-07-01 talk-fscd/main.tex
update talk (pseudo-final version)

\documentclass[11pt]{beamer}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{sourcesanspro}
\usepackage{sourcecodepro}
\usepackage{euler}
\usepackage[normalem]{ulem}
\usepackage{natbib}
\usepackage{apalike}
% \usepackage{bibentry}
% \usepackage{enumitem}
\usepackage[font={scriptsize},labelfont={scriptsize}]{caption}
\usepackage{lmodern,tgtermes,tabularx,ragged2e}
% \newcolumntype{Y}{>{\arraybackslash\RaggedRight}X}
% \newcolumntype{P}[1]{>{\arraybackslash\RaggedRight}p{#1}}
\usepackage{hhline}
\usepackage{booktabs}
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\usepackage{makecell}
\usepackage{pdfpages}
% \usepackage[overlay,absolute]{textpos}
%   \setlength{\TPHorizModule}{1mm}
%   \setlength{\TPVertModule}{1mm}
\usepackage{graphicx}

@@

\let\L=\lstinline
\def\lstlanguagefiles{defManSSR.tex}
\lstset{language=SSR}
\lstset{basicstyle=\footnotesize\ttfamily,breaklines=true}
\lstset{framextopmargin=50pt,frame=bottomline}
\lstset{moredelim=[is][\color{red}\bfseries\ttfamily\underbar]{|*}{*|}}
\lstset{moredelim=[is][\color{blue}\bfseries\ttfamily]{/*}{*/}}

@@

  \begin{itemize}
  \item A \textbf{carrier} in Set / Type,
  \item A set of \textbf{constants} in the carrier, and \textbf{operations},
  \item Proofs of the \textbf{axioms} of the structure
  \end{itemize}

  \pause

\begin{lstlisting}
Record is_ring R := mk_ring {
    zero : R; add : R -> R -> R; opp : R -> R;
    one : R;  mul : R -> R -> R;
    addrA : associative add;
    addrC : commutative add;
    add0r : left_id zero add;
    addNr : left_inverse zero opp add;
    mulrA : associative mul;
    mul1r : left_id one mul;
    mulr1 : right_id one mul;
    mulrDl : left_distributive mul add;
    mulrDr : right_distributive mul add;
  }.
\end{lstlisting}

@@

\begin{frame}
  \frametitle{Implementations in DTT (unbundled classes)}

@@

\begin{frame}
  \frametitle{Implementations in DTT (semi-bundled classes)}

@@

\begin{frame}
  \frametitle{Implementations in DTT (bundled record)}

@@

\begin{frame}
  \frametitle{Implementations in DTT (packed classes)}

@@

  A variety of representations:

  % more details comming
  \begin{itemize}
  \item {\sc Coq/Mathcomp}:     Classes packed in (canonical) structures
  \item {\sc Coq/Math-Classes}: Fully unbundled (typeclass) records $+$
                                special case for varieties.
  \item {\sc Lean/Mathlib}:     Variably-bundled (typeclass) records.
  \item {\sc Agda}:             bundled and semi-bundled records.
  \end{itemize}
  \vfill
  \pause

  Many other possibilities:
  \begin{itemize}
  \item Modules a la Ocaml \emph{(not first class!)},
  \item Fully-bundled typeclasses \emph{(bad!)},
  \item Telescopes \emph{(bad!)},
  \item Records without inference \emph{(tedious!)}, ...
  \end{itemize}
  \vfill
  \pause

\center{  \textbf{Representations work hand in hand with an inference
  mechanism.}}

@@

\begin{frame}
  \frametitle{Inference of structures}

  \begin{itemize}
  \item {\sc Coq/Mathcomp}:     canonical instances $+$ coercions $+$ checker
  \item {\sc Coq/Math-Classes}: typeclass instances $+$ hint extern
  \item {\sc Lean/Mathlib}:     typeclass instances $+$ linter
  \item {\sc Agda}:             \L{open} and renaming directives
  \end{itemize}

  \vfill
  \pause
  None of these encoding are straightforward, they all need
  expert knowledge or checkers/linters, and additionally

  \begin{itemize}
  \item Some encodings are unnecessarily verbose,
  \item Some known design problems might be detected too late
    (e.g. priority of instance, typeclass indexing, forgetful
    inheritance, etc)
  \end{itemize}

@@

  Purpose:
  \begin{itemize}
  \item factor theorems across instances, using the \textbf{theory} of
    each structure,
  \item \textbf{automatically find} which structures hold on which types.
  \end{itemize}

@@

  Requirements:
  \begin{itemize}
  \item declare a \textbf{new instance},
  \pause
  \item declare a \textbf{new structure}
    \begin{itemize}
    \item above, below or in the middle
    \item handle diamonds (e.g. monoid, group, commutative or not),
    \item by amending existing code, or not,
    \end{itemize}
  \pause
  \item \textbf{predictability} of inferred instance,
  \pause
  \item \textbf{robustness} of user code with regard to \textit{new declarations}.
  \end{itemize}

@@

\begin{frame}
  \frametitle{Hierarchy Builder in theory}

  \begin{enumerate}
  \item \textbf{Hierarchy Builder provides a DSL to generates/extends a
      hierarchy from minimal input.}
    \vfill
  \item \textbf{Hierarchy Builder lets you amend a hierarchy without
      breaking your code.}
  \end{enumerate}

@@

  That way, Hierarchy Builder is fully in control of the design
  patterns used throughout your library.
\end{frame}

@@

\begin{frame}
  \frametitle{Structure extension vs Structure entailment}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{center}
        {\bf \emph{Structure extension}}
      \end{center}
    \end{column}
    \begin{column}{0.5\textwidth}
      \begin{center}
        {\bf \emph{Structure extension}}
      \end{center}
    \end{column}
  \end{columns}
  \vfill
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item \textbf{Compositional}: no need to start from scratch every time.
        (E.g. the product of two groups is a group)
        \pause\vfill
      \item \textbf{Noisy}: changes the internal definition of a structure.
        (E.g. defining a commutative monoid from a monoid, one gets an unnecessary axiom),
        \pause\vfill
      \item \textbf{Non-robust}: breakage of user code when adding new
        intermediate structures, \pause\vfill
      \end{itemize}
    \end{column}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item \textbf{More flexible}: no need to cut structures
        into small bits,
        \pause\vfill
      \item \textbf{Robust}: lets us fix the operations and axioms
        once and for all.
        \pause\vfill
      \item \textbf{Not suitable for inference}: Major breakage when
        arbitrary entailment is automatic. (cf IJCAR \emph{Formalizing
          functional analysis structures in dependent type theory)}
        \pause\vfill
      \end{itemize}
    \end{column}
  \end{columns}
  \vfill

@@

  The best of two the worlds:
  \begin{itemize}
  \item \textbf{Extension}, through \emph{mixins} for \textbf{internal declaration} and
    \textbf{automatic inference}

  \item \textbf{Entailment}, through \emph{factories} for any other use.

    Factories require mixins and can produces others.
    (e.g. a full axiomatic can provide all the pieces)
  \end{itemize}
  \vfill

  Five commands:
  \begin{enumerate}
  \item \L{HB.mixin     Record axioms T := \{..\}.}
  \item \L{HB.factory   Record axioms T := \{..\}.}
  \item \L{HB.builder   Context       T (f : axioms T). ... HB.end.}
  \item \L{HB.structure Definition    S := \{ T & axioms T \}}
  \item \L{HB.instance  Definition    f := Axioms X ...}
  \end{enumerate}
  \vfill
  \begin{center}
    \url{https://github.com/math-comp/hierarchy-builder}
  \end{center}

@@

\begin{frame}[fragile]
  \frametitle{A very short example}

\begin{lstlisting}
HB.mixin Record is_monoid (M : Type) := {
  zero : M;
  add : M -> M -> M;
  addrA : associative add;   (* add is associative. *)
  add0r : left_id zero add;  (* zero is the neutral *)
  addr0 : right_id zero add; (*    element wrt add. *)
}.
HB.structure Definition Monoid := { M & is_monoid M }.

HB.instance Definition Z_Monoid_axioms : is_monoid Z :=
  is_monoid.Build Z 0%Z Z.add
    Z.add_assoc Z.add_0_l Z.add_0_r.
\end{lstlisting}
  \vfill

  See a full demo during the Coq workshop.
\end{frame}

@@

  We split the monoid structure into a semi-group and a monoid
  \begin{lstlisting}
HB.mixin Record is_semigroup (S : Type) := {
  add : S -> S -> S;
  addrA : associative add;   (* add is associative. *)
}.
HB.structure Definition SemiGroup :=
  { S & is_semigroup S }.

HB.mixin Record monoid_of_semigroup (M : Type) := {
  zero : M;
  add0r : left_id zero add;  (* zero is the neutral *)
  addr0 : right_id zero add; (*    element wrt add. *)
}.
HB.structure Definition Monoid :=
  { M & monoid_of_semigroup M }.
\end{lstlisting}
\center{\textbf{But we must provide \L{is_monoid} again.}}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Recovering \L{is_monoid}}

  It becomes a \emph{factory}.
\begin{lstlisting}
HB.factory Record is_monoid (M : Type) := {
  zero : M;
  add : M -> M -> M;
  addrA : associative add;
  add0r : left_id zero add;
  addr0 : right_id zero add;
}.

HB.builder Context (M : Type) (f : is_monoid M) :=
  HB.instance Definition is_monoid_semigroup :
    is_semigroup M := ...
  HB.instance Definition is_monoid_monoid :
    monoid_of_semigroup M := ...
HB.end
\end{lstlisting}
\end{frame}

@@

@@

\begin{frame}
  \frametitle{Future work on Hierarchy Builder}
  \begin{itemize}
  \item Adding support for parameters. (debugging phase in progress)
    \vfill
  \item Detecting and fixing competing inheritance paths.
    \vfill
  \item Generating hierarchies of morphisms from structures.
    \vfill
  \item Generating hierarchies of subobjects from structures.
    \vfill
  \item Supporting multiple instances on the same carrier.
    \vfill
  \item Replacing all uses in math-comp and extensions.
    \vfill
  \item Get better error messages.
  \end{itemize}
\end{frame}

>>>>

\documentclass[11pt]{beamer}
\usepackage[english]{babel}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{sourcesanspro}
\usepackage{sourcecodepro}
\usepackage{euler}
\usepackage[normalem]{ulem}
\usepackage{natbib}
\usepackage{apalike}

% \usepackage{bibentry}
% \usepackage{enumitem}
\usepackage[font={scriptsize},labelfont={scriptsize}]{caption}
\usepackage{lmodern,tgtermes,tabularx,ragged2e}
% \newcolumntype{Y}{>{\arraybackslash\RaggedRight}X}
% \newcolumntype{P}[1]{>{\arraybackslash\RaggedRight}p{#1}}
\usepackage{hhline}
\usepackage{booktabs}
\usepackage{array}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\usepackage{makecell}
\usepackage{pdfpages}
% \usepackage[overlay,absolute]{textpos}
%   \setlength{\TPHorizModule}{1mm}
%   \setlength{\TPVertModule}{1mm}
\usepackage{graphicx}

@@

\let\L=\lstinline
\def\lstlanguagefiles{defManSSR.tex}
\lstdefinelanguage{Prolog}
{
    basicstyle = \ttfamily\color{blue},
    moredelim = [s][\color{black}]{(}{)},
    literate =
        {:-}{{\textcolor{black}{:-}}}2
        {,}{{\textcolor{black}{,}}}1
        {.}{{\textcolor{black}{.}}}1
        {o:}{{\textcolor{black}{o:}}}1
        {i:}{{\textcolor{black}{o:}}}1
}

\lstset{language=SSR}
\lstset{basicstyle=\footnotesize\ttfamily,breaklines=true}
\lstset{framextopmargin=50pt,frame=bottomline}
\lstset{moredelim=[is][\color{red}\bfseries\ttfamily\underbar]{|*}{*|}}
\lstset{moredelim=[is][\color{blue}\bfseries\ttfamily]{/*}{*/}}

@@

  Standard definition:
  \begin{itemize}
  \item A \textbf{carrier} in Set / Type,
  \item A set of \textbf{constants} in the carrier, and \textbf{operations},
  \item Proofs of the \textbf{axioms} of the structure
  \end{itemize}

  E.g. an (additive) monoid is given by
  \begin{itemize}
  \item a carrier \L{T : Type},
  \item a constant \L{zero : T} and a binary operation %
    \L{add : T -> T -> T}
  \item three axioms: \\
    associativity of the addition, left and right neutrality of zero.
  \end{itemize}

@@

\begin{frame}[fragile]
  \frametitle{Implementations in DTT (unbundled classes)}

\begin{lstlisting}
Class |*is_monoid*| T (zero : T) (add : T -> T -> T) := {
    addrA : associative add;
    add0r : left_id zero add;
    add0r : right_id zero add;
  }.
\end{lstlisting}

@@

\begin{frame}[fragile]
  \frametitle{Implementations in DTT (semi-bundled classes)}

\begin{lstlisting}
Class |*is_monoid*| (T : Type) : Type := {
    zero  : T;
    add   : T -> T -> T;
    addrA : associative add;
    add0r : left_id zero add;
    add0r : right_id zero add;
  }.
\end{lstlisting}

\vfill
  \begin{onlyenv}<2>
\begin{lstlisting}
Class |*is_group*| (T : Type) : Type :=
  { zero : T;  add : T -> T -> T; opp : T -> T; .. }.
\end{lstlisting}
  \end{onlyenv}
  \begin{onlyenv}<3>
\begin{lstlisting}
Class |*group_of_monoid*| T : |*is_monoid*| T -> Type :=
   { opp : T -> T; .. }.
\end{lstlisting}
  \end{onlyenv}

@@

\begin{frame}[fragile]
  \frametitle{Implementations in DTT (bundled record)}

\begin{lstlisting}
Structure |*monoidType*| : Type := {
    sort  :> Type;
    zero  : sort;
    add   : sort -> sort -> sort;
    addrA : associative add;
    add0r : left_id zero add;
    add0r : right_id zero add;
  }.
\end{lstlisting}

\end{frame}
\begin{frame}[fragile]
  \frametitle{Implementations in DTT \\ \hfill (simplified packed classes)}

\begin{lstlisting}
Class |*is_monoid*| (T : Type) : Type := {
    zero  : T;
    add   : T -> T -> T;
    addrA : associative add;
    add0r : left_id zero add;
    add0r : right_id zero add;
  }.
\end{lstlisting}

\begin{lstlisting}
Structure |*monoidType*| : Type := {
    sort  :> Type;
    class : |*is_monoid*| sort;
  }.
\end{lstlisting}

@@

\begin{frame}[fragile]
  \frametitle{Implementations in DTT (packed classes)}

\begin{lstlisting}
Record |*is_monoid*| (T : Type) : Type := { zero ; ..}.

Structure |*monoidType*| : Type :=
  { sort :> Type;     class : |*is_monoid*| sort }.
\end{lstlisting}

\begin{lstlisting}
Record |*group_of_monoid*| T : |*is_monoid*| T -> Type := ...

Record |*is_group*| (T : Type) := {
    monoid_of_group : |*is_monoid*| T;
    group_of_group  : |*group_of_monoid*| T monoid_of_group
  }.

Structure |*groupType*| : Type :=
  { sort :> Type;     class : |*is_group*| sort }.
\end{lstlisting}

\begin{frame}
  \frametitle{Implementation in DTT (other)}

  Many other possibilities:
  \vfill
  \begin{itemize}
  \item Modules a la {\sc OCaml} \emph{(not first class in {\sc Coq}!)},
  \vfill
  \item Fully-bundled typeclasses \emph{(bad!)},
  \vfill
  \item Telescopes \emph{(bad!)},
  \vfill
  \item Records without inference \emph{(tedious!)},
  \vfill
  \item ...
  \end{itemize}

@@

  The variety of representations is out there!

  % more details comming
  \begin{itemize}
  \item {\sc Coq/Mathcomp}:     Packed classes\only<3>{\alert{ inside canonical
    structures}}.
\item {\sc Coq/Math-Classes}: Fully unbundled \alt<3>{\alert{type classes}}{records} \\
    \hfill ($+$ special case for varieties).
  \item {\sc Lean3/Mathlib}:     Semi-bundled \alt<3>{\alert{type classes}}{records}.
  \item {\sc Agda}:             Bundled and semi-bundled records.
  \end{itemize}
  \vfill
  \pause

  \vfill
  \pause

\center{\textbf{Representations work hand in hand with an inference
  mechanism.}}

@@

\begin{frame}
  \frametitle{More than ``just records''}

  \begin{itemize}
  \item {\sc Coq/Mathcomp}:     canonicals \alert<1>{$+$ heavy boilerplate $+$ checker}
  \item {\sc Coq/Math-Classes}: type classes \alert<1>{$+$ boilerplate $+$ hints}
  \item {\sc Lean3/Mathlib}:     type classes \alert<1>{$+$ priorities $+$ linter}
  \item {\sc Agda}:             records \alert<1>{$+$ open and renaming directives}
  \end{itemize}

  \vfill
  \pause
  \vfill

  None of these encoding are straightforward:
  \begin{itemize}
  \item they all need expert knowledge and/or checkers/linters,
  \item some encodings are unnecessarily verbose,
  \item some known design problems might be detected too late
    (e.g. priority of instance, typeclass indexing, forgetful
    inheritance, etc)
  \end{itemize}

@@

  Purpose:
  \begin{itemize}
  \item \textbf{factor theorems}, using the \emph{theory} of each structure,
  \item \textbf{automatically find} which structures hold on which types.
  \end{itemize}

@@

  Requirements:
  \begin{itemize}
  \item declare a \textbf{new instance},
  \pause
  \item declare a \textbf{new structure}
    \begin{itemize}
    \item above, below or in the middle
    \item handle diamonds (e.g. monoid, group, commutative or not),
    \item by amending existing code, or not,
    \end{itemize}
    \pause
  \item provide \textbf{several ways} to instantiate them
  \pause
  \item \textbf{predictability} of inferred instance,
  \pause
  \item \textbf{robustness} of user code with regard to \textit{new declarations}.
  \end{itemize}

@@

\begin{frame}
  \frametitle{Hierarchy Builder in two bullets}

  \begin{enumerate}
  \item \textbf{Hierarchy Builder provides a DSL to generate and extend a
      hierarchy from minimal input.}
    \vfill
  \item \textbf{Hierarchy Builder lets you amend a hierarchy without
      breaking your code.}
  \end{enumerate}

@@

  Hierarchy Builder takes care of the design pattern used throughout
  your library.
\end{frame}

@@

\begin{frame}
  \frametitle{Structure extension vs Structure entailment}
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{center}
        {\bf \emph{Structure extension}}
      \end{center}
    \end{column}
    \begin{column}{0.5\textwidth}
      \begin{center}
        {\bf \emph{Structure entailment}}
      \end{center}
    \end{column}
  \end{columns}
  \vfill
  \begin{columns}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item \textbf{Compositional}: no need to start from scratch every time.
        (E.g. the product of two groups is a group)
        \pause\vfill
      \item \textbf{Noisy}: changes the internal definition of a structure.
        (E.g. defining a commutative monoid from a monoid, one gets an unnecessary axiom),
        \pause\vfill
      \item \textbf{Non-robust}: breakage of user code when adding new
        intermediate structures, \pause\vfill
      \end{itemize}
    \end{column}
    \begin{column}{0.5\textwidth}
      \begin{itemize}
      \item \textbf{Flexible}: no need to cut structures
        into small bits,
        \pause\vfill
      \item \textbf{Robust}: lets us fix the operations and axioms
        once and for all.
        \pause\vfill
      \item \textbf{Not suitable for inference}: Major breakage when
        arbitrary entailment is automatic. (cf IJCAR \emph{Competing
          Inheritance Paths in Dependent Type Theory)} \pause\vfill
      \end{itemize}
    \end{column}
  \end{columns}
  \vfill

@@

  The best of two the worlds:
  \begin{itemize}
  \item \textbf{Extension}, through \emph{mixins} for \textbf{automatic inference}

  \item \textbf{Entailment}, through \emph{factories} for
    \textbf{smart instantiation}

    % Factories require mixins and can produces others.
    % (e.g. a full axiomatic can provide all the pieces)
  \end{itemize}
  \vspace{2em}
  \pause
  \vfill

  Five primitives:
  \begin{enumerate}
  \item \L{HB.mixin     Record |*<mixin name>*|$ $ T of |*<dependencies>*| := \{..\}.}
    \vspace{1em}
  \item \L{HB.factory   Record |*<factory name>*|$ $ T of |*<dependencies>*| := \{..\}.}
  \item \L{HB.builders   Context       T (f : |*<factory name>*|$ $ T). ... HB.end.}
    \vspace{1em}
  \item \L{HB.structure Definition    |*<structure name>*|$ $ :=} \L{\{ T & |*<dependencies>*| \}}
  \item \L{HB.instance  Definition    |*<name>*|$ $ : |*<axioms name>*| |*<type>*| := ...}
  \end{enumerate}
  \vfill

  \pause
  \begin{center}
    see \url{https://github.com/math-comp/hierarchy-builder}
  \end{center}

@@

\begin{frame}[fragile]
  \frametitle{A very short example}
{\scriptsize\url{https://github.com/math-comp/hierarchy-builder/tree/master/FSCD2020_talk}}

\begin{lstlisting}
HB.mixin Record |*is_monoid*| (M : Type) := {
  zero  : M;
  add   : M -> M -> M;
  addrA : associative add;   (* add is associative. *)
  add0r : left_id  zero add; (* zero is the neutral *)
  addr0 : right_id zero add; (*    element wrt add. *)
}.
HB.structure Definition |*Monoid*| := { M & |*is_monoid*| M }.

HB.instance Definition Z_is_monoid : |*is_monoid*| Z
  := |*is_monoid*|.Build Z 0%Z Z.add
    Z.add_assoc Z.add_0_l Z.add_0_r.
\end{lstlisting}
  \vfill

  See a bigger demo during the Coq workshop.
\end{frame}

@@

  We split the monoid structure into a semi-group and a monoid
\begin{lstlisting}
HB.mixin Record |*is_semigroup*| (S : Type) := {
  add   : S -> S -> S;
  addrA : associative add;
}.
HB.structure Definition |*SemiGroup*| :=
  { S & |*is_semigroup*| S }.
\end{lstlisting}
\begin{lstlisting}
HB.mixin Record |*monoid_of_semigroup*| (M : Type)
  & |*is_semigroup*| M := {
  zero  : M;
  add0r : left_id  zero add;
  addr0 : right_id zero add;
}.
HB.structure Definition |*Monoid*| :=
  { M & |*monoid_of_semigroup*| M }.
\end{lstlisting}
  \begin{center}
    \textbf{But we must provide \L{|*is_monoid*|} again.}
  \end{center}
\end{frame}

\begin{frame}[fragile]
  \frametitle{Recovering the lost mixin (\L{is_monoid})}

  It becomes a \emph{factory} with the \textbf{exact} same contents as before
\begin{lstlisting}
HB.factory Record |*is_monoid*| (M : Type) := {
  zero  : M;
  add   : M -> M -> M;
  addrA : associative add;
  add0r : left_id  zero add;
  addr0 : right_id zero add;
}.
HB.builders Context (M : Type) (f : |*is_monoid*| M).
  HB.instance Definition is_monoid_semigroup
    : |*is_semigroup*| M := ... (* trivial *)
  HB.instance Definition is_monoid_monoid
    : |*monoid_of_semigroup*| M := ... (* trivial *)
HB.end
\end{lstlisting}
  \begin{center}
    \textbf{Factories can only be used at instantiation time:}
  \end{center}
\begin{lstlisting}
HB.instance Definition Z_is_monoid : |*is_monoid*| Z := ...
\end{lstlisting}
\end{frame}

@@

  \textbf{{\sc Elpi} is a programming language,}
  \begin{itemize}
  \item prolog-like: \textbf{programs and data are clauses}
  \item with binders, unification and constraints
    \pause
  \item capable if representing {\sc Coq} terms in HOAS, its typing
    judgements, evaluation and unification.
  \end{itemize}
    \pause
    \vfill

  \textbf{{\sc Coq-Elpi} is a plugin for {\sc Coq}} that lets one use {\sc Elpi} as a
    meta-programming language, \pause in particular
  \begin{itemize}
  \item one can write new commands and tactics,
  \item one can add new definitions, inductive, sections, modules, etc
    to the environment,
  \item one can maintain databases across {\sc Coq} files
  \end{itemize}

\begin{frame}[fragile]
  \frametitle{Two main HB databases}

  \begin{itemize}
  \item The predicate \L{from} stores an association between a factory
    \L{F}, a mixin \L{M} and the term \L{B} that can be used to build
    mixin \L{M} from factory \L{F}.
\begin{lstlisting}[language=Prolog, basicstyle=\footnotesize]
pred from o:factoryname, o:mixinname, o:term.
\end{lstlisting}
\vfill
  \item The predicate {\footnotesize\tt factory-requires} stores an
    association between a factory and a list of mixins that are
    pre-requisites to inhabiting this factory.
\begin{lstlisting}[language=Prolog, basicstyle=\footnotesize]
pred factory-requires o:factoryname, o:list mixinname.
\end{lstlisting}
    e.g. \L{group_of_monoid T} has the prerequisite that \L{T} is a
    monoid.
  \end{itemize}

@@

\begin{frame}
  \frametitle{Future work on Hierarchy Builder}
  \begin{itemize}
  \item Adding support for parameters. (debugging phase in progress)
    \vfill
  \item Detecting and fixing competing inheritance paths.
    \vfill
  \item Generating hierarchies of morphisms from structures.
    \vfill
  \item Generating hierarchies of subobjects from structures.
    \vfill
  \item Supporting multiple instances on the same carrier.
    \vfill
  \item Replacing all uses in math-comp and extensions. (just started)
    \vfill
  \item Get better error messages. (work in progress)
  \end{itemize}
\end{frame}

\begin{frame}
  \begin{center}
   {\huge Thanks! Questions?}
  \end{center}
\end{frame}
